### 2013-09-23 image_proc_methods.tex
updated with all of the latest data
new b-mode and arfi segs fig included

\subsection{Image Zonal Anatomy Segmentation and 3D Model Rendering}
Axial MR T2WI images were manually segmented using the smooth polygon tool in
ITK-SNAP~\cite{Yushkevich2006}, using unique labels for the PZ, CG and AFS. The
gland was segmented from base to apex.  The base was identified below the
bladder, and subsequent images were segmented until the last slice with visible
prostatic tissue was identified caudally. The CG, PZ and AFS were segmented
independently according to their well-established anatomical characteristics on
T2WI.~\cite{Verma2011,Jung2012,Poon1985,Hricak2007,Bonekamp2011} The PZ was
identified by its homogenous high signal intensity on T2WI, which is usually
similar to that of the nearby periprostatic fat. The CG was visualized and
delineated based on its heterogeneous and lower signal intensity as well as its
location. Although not readily visible on every case, the AFS was identified by
its low T2 signal intensity and its location anterior to the central gland.

@@

\emph{CO-AUTHOR QUESTION: CAN WE EASILY DELINEATE OUR SEGMENTATION CRITERIA?}

>>>>

\subsection{Image Zonal Anatomy Segmentation and 3D Model Rendering}
Axial MR T2WI images were manually segmented using the smooth polygon tool in
ITK-SNAP~\cite{Yushkevich2006}, using unique labels for the PZ, CG and AFS. The
gland was segmented from base to apex.  The base was identified below the
bladder, and subsequent images were segmented until the last slice with visible
prostatic tissue was identified caudally. The CG, PZ and AFS were segmented
independently according to their well-established anatomical characteristics on
T2WI.~\cite{Verma2011,Jung2012,Poon1985,Hricak2007,Bonekamp2011} The PZ was
identified by its homogenous high signal intensity on T2WI, which is usually
similar to that of the nearby periprostatic fat. The CG was visualized and
delineated based on its heterogeneous and lower signal intensity as well as its
location (Figure~\ref{fig:mr_anatomy}). Although not readily visible on every
case, the AFS was identified by its low T2 signal intensity and its location
anterior to the central gland.

Figure~\ref{fig:mr_anatomy} shows the anatomic zones and some anatomic
orientation labels in the prostate of a representative study subject MR T2WI.  The
zonal anatomy of the prostate was manually segmented
(Figure~\ref{fig:mr_segs_vol}, bottom left) across the image stack, and 3D
models of the zonal anatomy volumes were rendered
(Figure~\ref{fig:mr_segs_vol}, top).

\input{fig_mr_anatomy}

\input{fig_mr_segs_vol}

@@

\input{fig_arfi_segs}

### 2013-09-23 results.tex
new b-mode and arfi segs fig included

\section{Results}\label{sect:results}

Figure~\ref{fig:mr_anatomy} shows the anatomic zones and some anatomic
orientation labels in the prostate of a representative study subject.  The
zonal anatomy of the prostate was manually segmented
(Figure~\ref{fig:mr_segs_vol}, bottom left) across the image stack, and 3D
models of the zonal anatomy volumes were rendered
(Figure~\ref{fig:mr_segs_vol}, top).

\input{fig_mr_anatomy}

\input{fig_mr_segs_vol}

The subvolumes associated with the zonal anatomy in each imaging modality were
measured (Figure~\ref{fig:mr_arfi_volumes}(a)), with moderate correlation
between the ARFI and MR total prostate gland volumes (R$^2$ = 0.68), with a
mean overestimation of of 36.7 $\pm$ 27.9\% by ARFI imaging compared to MR
volumes (Figure~\ref{fig:mr_arfi_volumes}(b)).  Central gland volumes were
slightly less correlated between ARFI and MR images (R$^2$ = 0.41) with no
significant mean over/under-estimation (2.1 $\pm$ 39.1\%), but significant
variability between the cases (Figure~\ref{fig:mr_arfi_volumes}(c)).
Table~\ref{tab:mr_arfi_volumes} has the individually-measured volumes for MR
and ARFI imaging for each study subject.

>>>>

\section{Results}\label{sect:results}
The subvolumes associated with the zonal anatomy in each imaging modality were
measured (Figure~\ref{fig:mr_arfi_volumes}(a)), with moderate correlation
between the ARFI and MR total prostate gland volumes (R$^2$ = 0.68), with a
mean overestimation of of 36.7 $\pm$ 27.9\% by ARFI imaging compared to MR
volumes (Figure~\ref{fig:mr_arfi_volumes}(b)).  Central gland volumes were
slightly less correlated between ARFI and MR images (R$^2$ = 0.41) with no
significant mean over/under-estimation (2.1 $\pm$ 39.1\%), but significant
variability between the cases (Figure~\ref{fig:mr_arfi_volumes}(c)).
Table~\ref{tab:mr_arfi_volumes} has the individually-measured volumes for MR
and ARFI imaging for each study subject.
